### 2025-03-14 paper/quarto_ecml/paper.tex
can now compute sensitivity to featues

Our key outcome of interest is how well do models perform with respect
to explainability (Def. \ref{def-explainability}). To this end, we focus
primarily on the plausibility and cost of faithfully generated
counterfactuals at test time. To measure the cost of counterfactuals, we
follow the standard convention of using distances (\(\ell_1\)-norm)
between factuals and counterfactuals as a proxy. For plausibility, we
assess how similar counterfactuals are to observed samples in the target
domain. We rely on the distance-based metric used by
\cite{altmeyer2024faithful},

@@

\begin{equation}\phantomsection\label{eq-impl-div}{
\text{IP}^*(\mathbf{X}^\prime,\mathbf{X}^+) = \text{MMD}(\mathbf{X}^\prime,\mathbf{X}^+)
}\end{equation} where \(\mathbf{X}^\prime\) denotes a set of multiple
counterfactuals and \(\text{MMD}(\cdot)\) is an unbiased estimate of the
squared population maximum mean discrepancy \cite{gretton2012kernel}.
The metric in Equation~\ref{eq-impl-div} is equal to zero iff the two
distributions are the same, \(\mathbf{X}^\prime=\mathbf{X}^+\).

>>>>

Our key outcome of interest is how well do models perform with respect
to explainability (Def. \ref{def-explainability}). To this end, we focus
primarily on the plausibility and cost of faithfully generated
counterfactuals at test time. To measure the cost of counterfactuals, we
follow the standard convention of using distances (\(\ell_1\)-norm)
between factuals and counterfactuals as a proxy. For plausibility, we
assess how similar counterfactuals are to observed samples in the target
domain, \(\mathbf{X}^+\subset\mathcal{X}^+\). We rely on the
distance-based metric used by \cite{altmeyer2024faithful},

@@

\begin{equation}\phantomsection\label{eq-impl-div}{
\text{IP}^*(\mathbf{X}^\prime,\mathbf{X}^+) = \text{MMD}(\mathbf{X}^\prime,\mathbf{X}^+)
}\end{equation} where \(\mathbf{X}^\prime\) denotes a collection of
counterfactuals and \(\text{MMD}(\cdot)\) is an unbiased estimate of the
squared population maximum mean discrepancy \cite{gretton2012kernel}.
The metric in Equation~\ref{eq-impl-div} is equal to zero iff the two
distributions are the same, \(\mathbf{X}^\prime=\mathbf{X}^+\).

### 2025-03-14 paper/sections/experiments.qmd
can now compute sensitivity to featues

Our key outcome of interest is how well do models perform with respect to explainability (Def. \ref{def-explainability}). To this end, we focus primarily on the plausibility and cost of faithfully generated counterfactuals at test time. To measure the cost of counterfactuals, we follow the standard convention of using distances ($\ell_1$-norm) between factuals and counterfactuals as a proxy. For plausibility, we assess how similar counterfactuals are to observed samples in the target domain. We rely on the distance-based metric used by @altmeyer2024faithful,

@@

$$
\text{IP}^*(\mathbf{X}^\prime,\mathbf{X}^+) = \text{MMD}(\mathbf{X}^\prime,\mathbf{X}^+)
$$ {#eq-impl-div}
where $\mathbf{X}^\prime$ denotes a set of multiple counterfactuals and $\text{MMD}(\cdot)$ is an unbiased estimate of the squared population maximum mean discrepancy [@gretton2012kernel]. The metric in @eq-impl-div is equal to zero iff the two distributions are the same, $\mathbf{X}^\prime=\mathbf{X}^+$.

>>>>

Our key outcome of interest is how well do models perform with respect to explainability (Def. \ref{def-explainability}). To this end, we focus primarily on the plausibility and cost of faithfully generated counterfactuals at test time. To measure the cost of counterfactuals, we follow the standard convention of using distances ($\ell_1$-norm) between factuals and counterfactuals as a proxy. For plausibility, we assess how similar counterfactuals are to observed samples in the target domain, $\mathbf{X}^+\subset\mathcal{X}^+$. We rely on the distance-based metric used by @altmeyer2024faithful,

@@

$$
\text{IP}^*(\mathbf{X}^\prime,\mathbf{X}^+) = \text{MMD}(\mathbf{X}^\prime,\mathbf{X}^+)
$$ {#eq-impl-div}
where $\mathbf{X}^\prime$ denotes a collection of counterfactuals and $\text{MMD}(\cdot)$ is an unbiased estimate of the squared population maximum mean discrepancy [@gretton2012kernel]. The metric in @eq-impl-div is equal to zero iff the two distributions are the same, $\mathbf{X}^\prime=\mathbf{X}^+$.
